---
title: "firingr8 Vignette"
author: "NICK, TURNER, and DANIEL"
date: "2024-05-03"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{firingr8 Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(firingr8)
```

# Hello there,
## This is a package for electrophysiology data that determines the firing rate (and a few other relevant pieces of data electrophysiologists like to know like halfwidth, sweep # with first action potential, and more!)
## Example usage is provided below using sample raw_ephys_data and identifiers_sample data.
```{r, eval = FALSE}
library(firingr8)

process_ephys_csv(csvfile_path = raw_ephys_data, experiment_identifier_path = identifiers_sample, output_path = ".")
```

## There is only one function which will require electrophysiology CSV data, an identifier dataset to determine which cell it is, and a selected output directory where it will make the folder to store the csv results and plot pdf it generates.

## Now, if you didn't change the output_path parameter from ".", go check your current directory where this folder was created based on title of CSV file which for the demo is raw_ephys_data.
```{r}
#output in example is "." which is current directory
getwd()
```