---
title: "firingr8 Vignette"
author: "NICK, TURNER, and DANIEL"
date: "2024-05-03"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{firingr8 Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(firingr8)
```

# Hello there,
## This is a package for electrophysiology data that determines the firing rate (and a few other parameters relavent too!)
## First, we will install this package then bring in the example data provided
```{r}
library(firingr8)
input <- raw_ephys_data
indentifiers <- identifiers_sample
```

## There is only one function which will require electrophysiology data, an identifier dataset to determine which cell it is, and a selected output
```{r, eval = FALSE}
process_ephys_csv(input, identifiers, ".")
```

## Now, go check your desktop to see the out put!
#Here is an example of the CSV file. 
```{r}
#output in example is "." which is present directory
getwd()
```